---
title: "How do news headlines develop in the week before Christmas 2021?"
subtitle: "The final project for the intro to data science course at Hertie"
output: 
  html_document:
    toc: FALSE
    df_print: paged
    number_sections: FALSE
    highlight: tango
    theme: "lumen"
    toc_depth: 3
    toc_float: false
    css: custom.css 
    self_contained: false
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r message = FALSE, warning = FALSE, include = FALSE}
## R Markdown

library(tidyverse)
library(fs)
library(tidytext)
library(fs)
library(plotly)
```

```{r message = FALSE, warning = FALSE, include = FALSE}
# importing csv files -----------------------------------------------------
file_paths <- fs::dir_ls("data")
file_paths

file_contents <- list()

for (i in seq_along(file_paths)) {
  file_contents[[i]] <- read_csv(
    file = file_paths[[i]]
  )
}

file_contents <- set_names(file_contents, file_paths)

headlines <- do.call(rbind, file_contents)
```

```{r message = FALSE, warning = FALSE, include = FALSE}
# cleaning with function - before tokenizing! --------------------------------------------------

clean_data <- function(x) { # x = path
  df <- x
  df$time <- as.POSIXct(df$time) %>% as.character() %>% str_replace_all("[ :]", "-")
  df <- select(df, -"...1")
  df$value <- gsub("<.*?>", "", df$value) # remove html tages
  df$value <- gsub(' +',' ', df$value) # remove more than one space
  df$value <- str_trim(df$value, side = c("both", "left", "right")) # remove spaces at start and end
  df[df == ""] <- NA #adding NAs to blank cells
  df <- na.omit(df) # remove NAs
  df <- rename(df, headline = value)
}

headlines <- clean_data(headlines)
```

```{r message = FALSE, warning = FALSE, include = FALSE}
headlines <- headlines %>% # maximum of 5500 headlines to avoid distortion, escecially of uk newspaper dailymail
  mutate(country = dplyr::case_when(name == "guardian" ~ "UK",
                                    name == "times" ~ "UK",
                                    name == "dailymail" ~ "UK",
                                    name == "independent" ~ "UK",
                                    name == "mirror" ~ "UK",
                                    name == "telegraph" ~ "UK",
                                    name == "nytimes" ~ "US",
                                    name == "wsj" ~ "US",
                                    name == "usatoday" ~ "US",
                                    name == "washingtonpost" ~ "US",
                                    name == "latimes" ~ "US",
                                    name == "tampabay" ~ "US",
                                    name == "heraldsun" ~ "Australia",
                                    name == "dailytelegraph" ~ "Australia",
                                    name == "financialreview" ~ "Australia",
                                    name == "couriermail" ~ "Australia",
                                    name == "westaustralian" ~ "Australia",
                                    name == "advertiser" ~ "Australia",
                                    name == "globeandmail" ~ "Canada",
                                    name == "thestar" ~ "Canada",
                                    name == "nationalpost" ~ "Canada",
                                    name == "torontosun" ~ "Canada",
                                    name == "vancouversun" ~ "Canada",
                                    name == "montrealgazette" ~ "Canada",
                                    name == "nzherald" ~ "New-Zealand",
                                    name == "waikato" ~ "New-Zealand",
                                    name == "businessreview" ~ "New-Zealand",
                                    name == "gisborneherald" ~ "New-Zealand",
                                    name == "dominionpost" ~ "New-Zealand",
                                    name == "thepress" ~ "New-Zealand"),
         
          format = dplyr::case_when(name == "dailymail" ~ "tabloid",
                                    name == "mirror" ~ "tabloid",
                                    name == "couriermail" ~ "tabloid",
                                    name == "westaustralian" ~ "tabloid",
                                    name == "advertiser" ~ "tabloid",
                                    name == "torontosun" ~ "tabloid",
                                    name == "nzherald" ~ "tabloid",
                                    TRUE ~ "broadsheet"),
         
         day = dplyr::case_when(grepl("2021-12-09", time) ~ "December 9",
                                grepl("2021-12-10", time) ~ "December 10",
                                grepl("2021-12-11", time) ~ "December 11",
                                grepl("2021-12-12", time) ~ "December 12",
                                grepl("2021-12-13", time) ~ "December 13",
                                grepl("2021-12-14", time) ~ "December 14",
                                grepl("2021-12-15", time) ~ "December 15",
                                grepl("2021-12-16", time) ~ "December 16"))

```

```{r message = FALSE, warning = FALSE, include = FALSE}
# ensuring balance --------------------------------------------------------



headlines_2 <- headlines %>% 
  group_by(name) %>% 
  slice(1:5000)

                                               
# tokenizing --------------------------------------------------------------

headlines_tok <- headlines %>% 
  unnest_tokens(output = word, input = headline) %>% 
  anti_join(stop_words) 


# clean -------------------------------------------------------------------

headlines_tok <- headlines_tok %>% 
  filter(!grepl('content|subscriber|read|star|10|9|6|min|l.a|wa|nz|canada|uk|west|tampa|times', word))  # dailymail uses the word star everywhore
```

```{r message = FALSE, warning = FALSE, include = FALSE}
## first graph: all newspapers in all countries

first_graph_data <- headlines_tok %>% 
  group_by(time, word) %>% 
  count(word, sort = TRUE, name = "n") 

first_graph_all <- first_graph_data %>% 
  filter(word == "christmas" | word == "covid" | word == "omicron" | word == "2021" | word == "home" |
         word == "party" | word == "f1" | word == "city" | word == "life" | word == "sex") %>% 
  ggplot(aes(x = time, y = n, group = word, colour = word)) +
  geom_line() +
  labs(title = "The frequency of the 10 most used deadlines, all newspapers") +
  ylab("Frequency") +
  xlab("Date") +
  scale_x_discrete(labels = c("2021-12-09-00-01-58"="Dec\n 9",  "2021-12-09-04-01-37"= "", "2021-12-09-08-01-21"= "", "2021-12-09-12-01-27"= "", "2021-12-09-16-01-24" = "", "2021-12-09-20-01-54" = "",
                              "2021-12-10-00-01-51"="Dec\n 10", "2021-12-10-04-01-37"= "", "2021-12-10-08-01-15"= "", "2021-12-10-12-01-29"= "", "2021-12-10-16-02-11" = "", "2021-12-10-20-01-28" = "", 
                              "2021-12-11-00-01-39"="Dec\n 11", "2021-12-11-04-01-51"= "", "2021-12-11-08-01-28"= "", "2021-12-11-12-01-32"= "", "2021-12-11-16-02-28" = "", "2021-12-11-20-01-38" = "",
                              "2021-12-12-00-01-28"="Dec\n 12", "2021-12-12-04-01-25"= "", "2021-12-12-08-01-14"= "", "2021-12-12-12-01-26"= "", "2021-12-12-16-01-27" = "", "2021-12-12-20-01-45" = "",
                              "2021-12-13-00-01-47"="Dec\n 13", "2021-12-13-04-01-19"= "", "2021-12-13-08-01-22"= "", "2021-12-13-12-01-25"= "", "2021-12-13-16-01-32" = "", "2021-12-13-20-01-28" = "",
                              "2021-12-14-00-02-06"="Dec\n 14", "2021-12-14-04-01-58"= "", "2021-12-14-08-01-30"= "", "2021-12-14-12-01-57"= "", "2021-12-14-16-02-10" = "", "2021-12-14-20-01-33" = "",
                              "2021-12-15-00-01-35"="Dec\n 15", "2021-12-15-04-01-28"= "", "2021-12-15-08-01-29"= "", "2021-12-15-12-01-34"= "", "2021-12-15-16-01-52" = "", "2021-12-15-20-01-35" = "")) +
  theme(axis.ticks = element_blank()) +
  theme_minimal()
                              

```
   
```{r message = FALSE, warning = FALSE, include = FALSE}
## second graph: all newspapers in the US 

second_graph_us_data <- headlines_tok %>% 
  group_by(time, word) %>%
  filter(country == "US") %>% 
  count(word, sort = TRUE, name = "n") %>% 
  ungroup()

test <- second_graph_us_data %>% 
  group_by(word) %>% 
  arrange(desc(time)) %>% 
  ungroup() %>% 
  group_by(time) %>% 
  slice(1:10)

  
second_graph_us <- second_graph_us_data %>% 
  filter(word == "covid" | word == "biden" | word == "omicron" | word == "house" | word == "holiday" |
           word == "california" | word == "tornadoes" | word == "court" | word == "inflation" | word == "abortion") %>% 
  ggplot(aes(x = time, y = n, group = word, colour = word)) +
  geom_line() +
  geom_point(size = 0.4) +
  labs(title = "The frequency of the 10 most used deadlines, US newspapers") +
  ylab("Frequency") +
  xlab("Date") +
  scale_x_discrete(labels = c("2021-12-09-00-01-58"="Dec\n 9",  "2021-12-09-04-01-37"= "", "2021-12-09-08-01-21"= "", "2021-12-09-12-01-27"= "", "2021-12-09-16-01-24" = "", "2021-12-09-20-01-54" = "",
                              "2021-12-10-00-01-51"="Dec\n 10", "2021-12-10-04-01-37"= "", "2021-12-10-08-01-15"= "", "2021-12-10-12-01-29"= "", "2021-12-10-16-02-11" = "", "2021-12-10-20-01-28" = "", 
                              "2021-12-11-00-01-39"="Dec\n 11", "2021-12-11-04-01-51"= "", "2021-12-11-08-01-28"= "", "2021-12-11-12-01-32"= "", "2021-12-11-16-02-28" = "", "2021-12-11-20-01-38" = "",
                              "2021-12-12-00-01-28"="Dec\n 12", "2021-12-12-04-01-25"= "", "2021-12-12-08-01-14"= "", "2021-12-12-12-01-26"= "", "2021-12-12-16-01-27" = "", "2021-12-12-20-01-45" = "",
                              "2021-12-13-00-01-47"="Dec\n 13", "2021-12-13-04-01-19"= "", "2021-12-13-08-01-22"= "", "2021-12-13-12-01-25"= "", "2021-12-13-16-01-32" = "", "2021-12-13-20-01-28" = "",
                              "2021-12-14-00-02-06"="Dec\n 14", "2021-12-14-04-01-58"= "", "2021-12-14-08-01-30"= "", "2021-12-14-12-01-57"= "", "2021-12-14-16-02-10" = "", "2021-12-14-20-01-33" = "",
                              "2021-12-15-00-01-35"="Dec\n 15", "2021-12-15-04-01-28"= "", "2021-12-15-08-01-29"= "", "2021-12-15-12-01-34"= "", "2021-12-15-16-01-52" = "", "2021-12-15-20-01-35" = "")) +
  theme(axis.ticks = element_blank()) +
  theme_minimal() +
  scale_color_brewer(palette = "Set3")

          
```

```{r message = FALSE, warning = FALSE, include = FALSE}
## third graph: all newspapers in the UK
                       
third_graph_uk_data <- headlines_tok %>% 
  group_by(time, word) %>%
  filter(country == "UK") %>% 
  count(word, sort = TRUE, name = "n") %>% 
  ungroup()

test <- third_graph_uk_data %>% 
  group_by(word) %>% 
  arrange(desc(time)) %>% 
  ungroup() %>% 
  group_by(time) %>% 
  slice(1:10)

third_graph_uk <- third_graph_uk_data %>% 
  filter(word == "christmas" | word == "covid" | word == "party" | word == "boris" | word == "johnson" |
           word == "omicron" | word == "black" | word == "son" | word == "sex" | word == "home" |
           word == "love" | word == "daughter" | word == "verstappen" | word == "lewis" | word == "booster") %>% 
  ggplot(aes(x = time, y = n, group = word, colour = word)) +
  geom_line() +
  geom_point(size = 0.4) +
  labs(title = "The frequency of the 10 most used deadlines, UK newspapers") +
  ylab("Frequency") +
  xlab("Date") +
  scale_x_discrete(labels = c("2021-12-09-00-01-58"="Dec\n 9",  "2021-12-09-04-01-37"= "", "2021-12-09-08-01-21"= "", "2021-12-09-12-01-27"= "", "2021-12-09-16-01-24" = "", "2021-12-09-20-01-54" = "",
                              "2021-12-10-00-01-51"="Dec\n 10", "2021-12-10-04-01-37"= "", "2021-12-10-08-01-15"= "", "2021-12-10-12-01-29"= "", "2021-12-10-16-02-11" = "", "2021-12-10-20-01-28" = "", 
                              "2021-12-11-00-01-39"="Dec\n 11", "2021-12-11-04-01-51"= "", "2021-12-11-08-01-28"= "", "2021-12-11-12-01-32"= "", "2021-12-11-16-02-28" = "", "2021-12-11-20-01-38" = "",
                              "2021-12-12-00-01-28"="Dec\n 12", "2021-12-12-04-01-25"= "", "2021-12-12-08-01-14"= "", "2021-12-12-12-01-26"= "", "2021-12-12-16-01-27" = "", "2021-12-12-20-01-45" = "",
                              "2021-12-13-00-01-47"="Dec\n 13", "2021-12-13-04-01-19"= "", "2021-12-13-08-01-22"= "", "2021-12-13-12-01-25"= "", "2021-12-13-16-01-32" = "", "2021-12-13-20-01-28" = "",
                              "2021-12-14-00-02-06"="Dec\n 14", "2021-12-14-04-01-58"= "", "2021-12-14-08-01-30"= "", "2021-12-14-12-01-57"= "", "2021-12-14-16-02-10" = "", "2021-12-14-20-01-33" = "",
                              "2021-12-15-00-01-35"="Dec\n 15", "2021-12-15-04-01-28"= "", "2021-12-15-08-01-29"= "", "2021-12-15-12-01-34"= "", "2021-12-15-16-01-52" = "", "2021-12-15-20-01-35" = "")) +
  theme(axis.ticks = element_blank()) +
  theme_minimal()

   
```

```{r message = FALSE, warning = FALSE, include = FALSE}
fourth_graph_canada_data <- headlines_tok %>% 
  group_by(time, word) %>%
  filter(country == "Canada") %>% 
  count(word, sort = TRUE, name = "n") %>% 
  ungroup()

test <- fourth_graph_canada_data %>% 
  group_by(word) %>% 
  arrange(desc(time)) %>% 
  ungroup() %>% 
  group_by(time) %>% 
  slice(1:10)

fourth_graph_canada <- fourth_graph_canada_data %>% 
  filter(word == "covid" | word == "million" | word == "car" | word == "boycott" | word == "document" |
           word == "school" | word == "bill" | word == "study" | word == "weed" | word == "electric" |
           word == "holiday" | word == "health" | word == "omicron" | word == "vaccine" | word == "dies" |
           word == "change" | word == "pandemic" | word == "fiscal" | word == "policy" | word == "inflation") %>% 
  ggplot(aes(x = time, y = n, group = word, colour = word)) +
  geom_line() +
  geom_point(size = 0.4) +
  labs(title = "The frequency of the 10 most used deadlines, Canadian newspapers") +
  ylab("Frequency") +
  xlab("Date") +
  scale_x_discrete(labels = c("2021-12-09-00-01-58"="Dec\n 9",  "2021-12-09-04-01-37"= "", "2021-12-09-08-01-21"= "", "2021-12-09-12-01-27"= "", "2021-12-09-16-01-24" = "", "2021-12-09-20-01-54" = "",
                              "2021-12-10-00-01-51"="Dec\n 10", "2021-12-10-04-01-37"= "", "2021-12-10-08-01-15"= "", "2021-12-10-12-01-29"= "", "2021-12-10-16-02-11" = "", "2021-12-10-20-01-28" = "", 
                              "2021-12-11-00-01-39"="Dec\n 11", "2021-12-11-04-01-51"= "", "2021-12-11-08-01-28"= "", "2021-12-11-12-01-32"= "", "2021-12-11-16-02-28" = "", "2021-12-11-20-01-38" = "",
                              "2021-12-12-00-01-28"="Dec\n 12", "2021-12-12-04-01-25"= "", "2021-12-12-08-01-14"= "", "2021-12-12-12-01-26"= "", "2021-12-12-16-01-27" = "", "2021-12-12-20-01-45" = "",
                              "2021-12-13-00-01-47"="Dec\n 13", "2021-12-13-04-01-19"= "", "2021-12-13-08-01-22"= "", "2021-12-13-12-01-25"= "", "2021-12-13-16-01-32" = "", "2021-12-13-20-01-28" = "",
                              "2021-12-14-00-02-06"="Dec\n 14", "2021-12-14-04-01-58"= "", "2021-12-14-08-01-30"= "", "2021-12-14-12-01-57"= "", "2021-12-14-16-02-10" = "", "2021-12-14-20-01-33" = "",
                              "2021-12-15-00-01-35"="Dec\n 15", "2021-12-15-04-01-28"= "", "2021-12-15-08-01-29"= "", "2021-12-15-12-01-34"= "", "2021-12-15-16-01-52" = "", "2021-12-15-20-01-35" = "")) +
  theme(axis.ticks = element_blank()) +
  theme_minimal()

```

```{r message = FALSE, warning = FALSE, include = FALSE}
## fifth graph: all newspapers in Australia

fifth_graph_australia_data <- headlines_tok %>% 
  group_by(time, word) %>%
  filter(country == "Australia") %>% 
  count(word, sort = TRUE, name = "n") %>% 
  ungroup()

test <- fifth_graph_australia_data %>% 
  group_by(word) %>% 
  arrange(desc(time)) %>% 
  ungroup() %>% 
  group_by(time) %>% 
  slice(1:10)

fifth_graph_australia <- fifth_graph_australia_data %>% 
  filter(word == "covid" | word == "ashes" | word == "aussie" | word == "home" | word == "fight" |
           word == "omicron" | word == "shock" | word == "history" | word == "court" | word == "industry" |
           word == "city" | word == "christmas" | word == "car" | word == "life" | word == "summer" |
           word == "cricket" | word == "game" | word == "poms" | word == "death" | word == "border" |
           word == "kids") %>% 
  ggplot(aes(x = time, y = n, group = word, colour = word)) +
  geom_line() +
  geom_point(size = 0.4) +
  labs(title = "The frequency of the 10 most used deadlines, Australian newspapers") +
  ylab("Frequency") +
  xlab("Date") +
  scale_x_discrete(labels = c("2021-12-09-00-01-58"="Dec\n 9",  "2021-12-09-04-01-37"= "", "2021-12-09-08-01-21"= "", "2021-12-09-12-01-27"= "", "2021-12-09-16-01-24" = "", "2021-12-09-20-01-54" = "",
                              "2021-12-10-00-01-51"="Dec\n 10", "2021-12-10-04-01-37"= "", "2021-12-10-08-01-15"= "", "2021-12-10-12-01-29"= "", "2021-12-10-16-02-11" = "", "2021-12-10-20-01-28" = "", 
                              "2021-12-11-00-01-39"="Dec\n 11", "2021-12-11-04-01-51"= "", "2021-12-11-08-01-28"= "", "2021-12-11-12-01-32"= "", "2021-12-11-16-02-28" = "", "2021-12-11-20-01-38" = "",
                              "2021-12-12-00-01-28"="Dec\n 12", "2021-12-12-04-01-25"= "", "2021-12-12-08-01-14"= "", "2021-12-12-12-01-26"= "", "2021-12-12-16-01-27" = "", "2021-12-12-20-01-45" = "",
                              "2021-12-13-00-01-47"="Dec\n 13", "2021-12-13-04-01-19"= "", "2021-12-13-08-01-22"= "", "2021-12-13-12-01-25"= "", "2021-12-13-16-01-32" = "", "2021-12-13-20-01-28" = "",
                              "2021-12-14-00-02-06"="Dec\n 14", "2021-12-14-04-01-58"= "", "2021-12-14-08-01-30"= "", "2021-12-14-12-01-57"= "", "2021-12-14-16-02-10" = "", "2021-12-14-20-01-33" = "",
                              "2021-12-15-00-01-35"="Dec\n 15", "2021-12-15-04-01-28"= "", "2021-12-15-08-01-29"= "", "2021-12-15-12-01-34"= "", "2021-12-15-16-01-52" = "", "2021-12-15-20-01-35" = "")) +
  theme(axis.ticks = element_blank()) +
  theme_minimal()


```

```{r message = FALSE, warning = FALSE, include = FALSE}

sixth_graph_nz_data <- headlines_tok %>% 
  group_by(time, word) %>%
  filter(country == "New-Zealand") %>% 
  count(word, sort = TRUE, name = "n") %>% 
  ungroup()

test <- sixth_graph_nz_data %>% 
  group_by(word) %>% 
  arrange(desc(time)) %>% 
  ungroup() %>% 
  group_by(time) %>% 
  slice(1:20)

sixth_graph_nz <- sixth_graph_nz_data %>% 
  filter(word == "christmas" | word == "covid" | word == "gifts" | word == "business" | word == "spy" |
           word == "black" | word == "light" | word == "vaccine" | word == "plans" | word == "beijing" |
           word == "border" | word == "care" | word == "outbreak" | word == "travel" | word == "summer" |
           word == "orange" | word == "kiwi" | word == "guide") %>% 
  ggplot(aes(x = time, y = n, group = word, colour = word)) +
  geom_line() +
  geom_point(size = 0.4) +
  labs(title = "The frequency of the 10 most used deadlines, Australian newspapers") +
  ylab("Frequency") +
  xlab("Date") +
  scale_x_discrete(labels = c("2021-12-09-00-01-58"="Dec\n 9",  "2021-12-09-04-01-37"= "", "2021-12-09-08-01-21"= "", "2021-12-09-12-01-27"= "", "2021-12-09-16-01-24" = "", "2021-12-09-20-01-54" = "",
                              "2021-12-10-00-01-51"="Dec\n 10", "2021-12-10-04-01-37"= "", "2021-12-10-08-01-15"= "", "2021-12-10-12-01-29"= "", "2021-12-10-16-02-11" = "", "2021-12-10-20-01-28" = "", 
                              "2021-12-11-00-01-39"="Dec\n 11", "2021-12-11-04-01-51"= "", "2021-12-11-08-01-28"= "", "2021-12-11-12-01-32"= "", "2021-12-11-16-02-28" = "", "2021-12-11-20-01-38" = "",
                              "2021-12-12-00-01-28"="Dec\n 12", "2021-12-12-04-01-25"= "", "2021-12-12-08-01-14"= "", "2021-12-12-12-01-26"= "", "2021-12-12-16-01-27" = "", "2021-12-12-20-01-45" = "",
                              "2021-12-13-00-01-47"="Dec\n 13", "2021-12-13-04-01-19"= "", "2021-12-13-08-01-22"= "", "2021-12-13-12-01-25"= "", "2021-12-13-16-01-32" = "", "2021-12-13-20-01-28" = "",
                              "2021-12-14-00-02-06"="Dec\n 14", "2021-12-14-04-01-58"= "", "2021-12-14-08-01-30"= "", "2021-12-14-12-01-57"= "", "2021-12-14-16-02-10" = "", "2021-12-14-20-01-33" = "",
                              "2021-12-15-00-01-35"="Dec\n 15", "2021-12-15-04-01-28"= "", "2021-12-15-08-01-29"= "", "2021-12-15-12-01-34"= "", "2021-12-15-16-01-52" = "", "2021-12-15-20-01-35" = "")) +
  theme(axis.ticks = element_blank()) +
  theme_minimal()

```


## title {.tabset .tabset-fade .tabset-pills}
The headlines used in the main newspapers of the US, UK, Canada, Australia and New-Zealand between December 9 (0.00 CET) and December 16 (0.00 CET)

### All countries {.tabset .tabset-fade .tabset-pills}

```{r, out.width='100%'}
ggplotly(first_graph_all) %>% 
  partial_bundle()
```

It is evident that in all countries, the large majority of headlines relate to *Covid-19* and *Christmas*. In all countries, the usage of words related to these topics fluctuated heavily. This is due to the fact that new developments constantly arise with regards to these topics, such as: what will be the effect of the omicron variant and will we be able to visit our families during Christmas?

### US {.tabset .tabset-fade .tabset-pills}

#### All newspapers

```{r, out.width='100%'}
ggplotly(second_graph_us) %>% 
  partial_bundle()
```

#### NYtimes

```{r, out.width='100%'}

headlines_tok$number <- 1 

test_df <- headlines_tok %>% 
  filter(day == "December 9",
         country == "UK") %>% 
  group_by(word) %>% 
  summarise(occurrences=sum(number)) %>%
  arrange(desc(occurrences)) %>%
  slice(1:20)
  
ggplot(aes(x = word, y = occurences)) +
  geom_bar(stat = "identity")


  
  filter(day == "December 9") %>%
  count() %>% 
  arrange(desc(n)) %>% 
  slice(1:20)

filter(country == input$country & day ==input$day & format ==input$format & name ==input$name) %>% group_by(word) %>%
summarise(occurrences=sum(Number)) %>%
arrange(desc(occurrences)) %>%
top_n(input$select_topn) %>%
ungroup() %>%
ggplot(aes(x=word,
y=occurrences))



second_graph_us_data_nytimes <- headlines_tok %>% 
  filter(name == "nytimes") %>% 
  group_by(time, word) %>%
  count(word, sort = TRUE, name = "n") %>% 
  ungroup()

second_graph_us_nytimes <- second_graph_us_data_nytimes %>% 
  filter(word == "covid" | word == "aid" | word == "beatles" | word == "billionaire" | word == "court" |
           word == "democrats" | word == "omicron" | word == "schools" | word == "biden" | word == "inflation") %>% 
  ggplot(aes(x = time, y = n, group = word, colour = word)) +
  geom_line() +
  geom_point(size = 0.4) +
  labs(title = "The frequency of the 10 most used deadlines, us newspapers") +
  ylab("Frequency") +
  xlab("Date") +
  scale_x_discrete(labels = c("2021-12-09-00-01-58"="Dec\n 9",  "2021-12-09-04-01-37"= "", "2021-12-09-08-01-21"= "", "2021-12-09-12-01-27"= "", "2021-12-09-16-01-24" = "", "2021-12-09-20-01-54" = "",
                              "2021-12-10-00-01-51"="Dec\n 10", "2021-12-10-04-01-37"= "", "2021-12-10-08-01-15"= "", "2021-12-10-12-01-29"= "", "2021-12-10-16-02-11" = "", "2021-12-10-20-01-28" = "", 
                              "2021-12-11-00-01-39"="Dec\n 11", "2021-12-11-04-01-51"= "", "2021-12-11-08-01-28"= "", "2021-12-11-12-01-32"= "", "2021-12-11-16-02-28" = "", "2021-12-11-20-01-38" = "",
                              "2021-12-12-00-01-28"="Dec\n 12", "2021-12-12-04-01-25"= "", "2021-12-12-08-01-14"= "", "2021-12-12-12-01-26"= "", "2021-12-12-16-01-27" = "", "2021-12-12-20-01-45" = "",
                              "2021-12-13-00-01-47"="Dec\n 13", "2021-12-13-04-01-19"= "", "2021-12-13-08-01-22"= "", "2021-12-13-12-01-25"= "", "2021-12-13-16-01-32" = "", "2021-12-13-20-01-28" = "",
                              "2021-12-14-00-02-06"="Dec\n 14", "2021-12-14-04-01-58"= "", "2021-12-14-08-01-30"= "", "2021-12-14-12-01-57"= "", "2021-12-14-16-02-10" = "", "2021-12-14-20-01-33" = "",
                              "2021-12-15-00-01-35"="Dec\n 15", "2021-12-15-04-01-28"= "", "2021-12-15-08-01-29"= "", "2021-12-15-12-01-34"= "", "2021-12-15-16-01-52" = "", "2021-12-15-20-01-35" = "")) +
  theme(axis.ticks = element_blank()) +
  theme_minimal() +
  scale_color_brewer(palette = "Set3")

ggplotly(second_graph_us_nytimes) %>% 
  partial_bundle()

```

#### Wall Street Journal

#### LA Times

#### Tampala Bay





### UK {.tabset .tabset-fade .tabset-pills}

```{r, out.width='100%'}
ggplotly(third_graph_uk) %>% 
  partial_bundle()
```

#### The Guardian

hi

### Canada {.tabset .tabset-fade .tabset-pills}

```{r, out.width='100%'}
ggplotly(fourth_graph_canada) %>% 
  partial_bundle()
```

### Australia {.tabset .tabset-fade .tabset-pills}

```{r, out.width='100%'}
ggplotly(fifth_graph_australia) %>% 
  partial_bundle()
```

### New-Zealand {.tabset .tabset-fade .tabset-pills}

```{r, out.width='100%'}
ggplotly(sixth_graph_nz) %>% 
  partial_bundle()
```


## Analysis

We can summarize the week before Christmas 2021 with two words: *Covid-19* and *Christmas*. 












